What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2025-03-20 manuscript.Rmd
Addressing R1, comment 10

@@

Second, researchers need to take care with timing accuracy. Running studies on mod.
ern computers requires synchronizing multiple clocks, something that does not happen automatically. Failure to synchronize can result in substantial inaccuracies [@slim2022moving]. As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization. We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background. We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.

>>>>

Upon finishing calibration, participants were reminded to keep their head still for the remainder of the study.

@@

There are a number of other interventions that might increase precision and should be investigated. For instance, it is possible to monitor head distance in real time [for an example, see @jiang2021easyeyes]; doing so and providing real-time feedback to participants should diminish noise. It may also be possible to automatically detect challenges to calibration accuracy (such as poor lighting) and provide targeted feedback. These and other options should be investigated in order to determine how much they might improve precision.

Second, researchers need to take care with timing accuracy. Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically. Failure to synchronize can result in substantial inaccuracies [@slim2022moving]. As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization. We urge researchers to avoid using the current release of WebGazer.js as is, and instead either use jsPsych, our patch to WebGazer.js (https://github.com/brownhci/WebGazer/commit/35301e56c192ef265bb270873a6526205f183711), or other software that has been specifically documented as addressing common issues in timing for web-based eye-tracking.
Third, it is true for any eyetracker that precise data depends on good calibration, and good calibration depends in part on lighting and background. We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.
